Revision of MS #2018:11:32569:0:0:REVIEW

### 2019-02-09 docs/Manuscript.tex
Added comments by Sean, and new figure

\title{Spatial variation in allometric growth of invasive lionfish has
management implications}

@@

\begin{abstract}
Lionfish (\textit{Pterois volitans / miles}) are an invasive species in
the Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate total biomass estimates, which
depend on accurate estimates of allometric growth, but sedentary species
like lionfish often exhibit high levels of spatial variation in life
history characteristics. We reviewed 17 published length-weight
relationships for lionfish taken throughout their invasive range and
found regional differences that led to significant misestimates when
calculating weight from length observations. The spatial pattern we
observed is consistent with findings from other studies focused on
genetics or length-at-age. We show that the use of \textit{ex situ}
parameters can result in up to a threefold under- or overestimation of
total weight, but using parameters from nearby regions substantially
reduces this error. These findings can have implications for management
in terms of predicting effects on local ecosystems, evaluating the
effectiveness of removal programs, or estimating biomass available for
harvest.
\end{abstract}

@@

Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
in the Western Atlantic Ocean and Caribbean Sea, likely introduced
through release of aquarium-kept organisms \citep{betancurr_2011}.
Lionfish are the first invasive marine vertebrates established along
these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}, and
they have established invasive populations in coral reefs, estuaries,
mangroves, hard-bottomed areas, and mesophotic reefs
\citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
Their presence has been labeled as a major marine invasion because they
threaten local biodiversity, spread rapidly, and are difficult to manage
\citep{hixon_2016}.

@@

We reviewed 12 published studies and obtained 17 length-weight
relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}).
Study sites included North Carolina, the Northern and Southern Gulf of
Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman,
Jamaica, Bonaire, Puerto Rico, and Costa Rica
\citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
Unfortunately, we have access only to the summarized information
published in these studies - not the raw data used to make length-weight
calculations. We collected information on sex differentiation, location,
length and depth ranges, and sampling methods from each study when
available. Only two studies reported sex-specific length-weight
parameters \citep{aguilarperera_2016,fogg_2013}, so we assumed data were
reported for both sexes combined in all other studies. Reviewed studies
presented information for organisms ranging from 25-475 mm in Total
Length (\(TL\)) and were obtained at depths between 0.5 m and 57 m. Four
studies explicitly stated that their organisms were sampled with pole
spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016},
and six studies mentioned that some of their organisms were obtained
with pole spears (or other type of harpoon) but also hand-held nets or
fish traps
\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}.
Two studies did not specify how organisms were sampled
\citep{darling_2011,deleon_2013}.

@@

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here. Recall that the objective of this study is not to
describe variations between populations (which would require access to
raw data), but rather to assess how \emph{ex situ} parameter values
influence the accuracy of weight estimates for lionfish, using the
central Mexican Caribbean as a case study. Using each of the 18
parameter pairs, we estimated \(TW\) from the \(TL\) observations
collected in the central Mexican Caribbean (n = 109, with \(TL\) ranging
from 34 mm to 310 mm) and divided predicted weights by known observed
weights to obtain a simple measure of over- or underestimation.
Difference in mean weight ratios were tested with an analysis of
covariance (ANCOVA), where the sources of variation were the study and
\(TL\). Ratios were logit-transformed prior to analysis, and a
\emph{post-hoc} Tukey's test was used to identify groups where mean
ratios did not differ. All analyses were performed in R version 3.5.2
\citep{rcore_2018}. Raw data and code used in this work are available on
github at github.com/jcvdav/lionfish\_biometry.

\begin{table}[t]

\caption{\label{tab:unnamed-chunk-2}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
\centering
\begin{tabular}{llllrll}
\toprule
Region & Sex & n & a & b & \$R\textasciicircum{}2\$ & Reference\\
\midrule
Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
\addlinespace
GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
\addlinespace
Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
\addlinespace
Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
\bottomrule
\end{tabular}
\end{table}

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in coefficient values of \(a = 3.206e-06\) and
\(b = 3.235\) (\(R^2 = 0.977\), \(F_{1, 107} = 6928.67; p < 0.001\)).
The allometric factor (\(b\)) was significantly different from \(b = 3\)
(\(t_{107} = 6.04; p<0.001\)), corroborating that lionfish present
allometric growth. The length-weight coefficients estimated here were
within the range identified by studies from other regions (Table
\ref{tab:all_params}). Figure \ref{fig:l-w-carib} shows the relationship
between TL and TW for this region.

@@

There were significant differences in our predicted weights for the
central Mexican Caribbean when using each of the different pairs of
parameters (\(F_{17, 1943} = 24.96; p < 0.001\)). The lowest weight
estimates for the observed lengths resulted from using the allometric
parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
highest weight estimates came from the Western Atlantic with 73.76
\(\pm\) 96.11 g \citep{barbour_2011}. True observed weights had a mean
of 52.56 \(\pm\) 76.58 g. Weights predicted from these extreme
parameters correspond to predicted-to-observed weight ratios of 0.80
\(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively. The
largest under- and overestimations resulted in ratios of 0.36 and 3.51
of the actual observed weight, indicating that \emph{ex situ} parameters
can result in highly erroneous weight estimates.

Tukey's \emph{post-hoc} test suggested that weight ratios for the
central Mexican Caribbean were not different from those obtained with
parameters from Little Cayman, the Bahamas, and some sites in the Gulf
of Mexico (Tukey's HSD \(p > 0.05\)). All weight estimates using
parameters from the Gulf of Mexico and Western Atlantic were higher than
observed values, and only parameters from the Caribbean produced weights
smaller than observed (Fig \ref{fig:bio_ratio}). The regional average
(\(\pm\) SD) of predicted-to-observed weight ratios from these three
regions were 1.24 \(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\)
0.423 for the Gulf of Mexico, Western Atlantic, and Caribbean,
respectively. This suggests that the smallest errors are observed when
using parameters from other locations in the Caribbean.
Predicted-to-observed weight ratios are presented in Figure
\ref{fig:bio_ratio}.

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/pred_obs-1.pdf}
\caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
weight ratios for 18 pairs of allometric parameters. Blue circles
indicate median values and like letters indicate values that do not
differ significantly. For Sabido-Itza et al, 2016b, BC and PNAX make
reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak,
two sites for which they report parameters.}
\end{figure}

@@

Applying parameter estimates to lengths outside the range of lengths
originally used to estimate the parameters may also induce error. Our
smallest observed organism was 34 mm in \(TL\), and only two studies
estimated parametrs with smaller organisms
\citep{edwards_2014,sabidoitza_2016}. By contrast, our largest organism
had a \(TL\) of 310 mm, which is well within the range of all other
studies (the next smallest maximum length was 325 mm; See Supplementary
Table 2). Due to the power function describing the allometric
relationship (\emph{i.e.} Eq. 1), the error in weight estimates is
larger when extrapolation is done for lengths that are larger than the
maximum length used to estimate the parameters.

The results presented here have key implications for management. For
example, \citet{edwards_2014} simulated a lionfish culling program under
two scenarios, one using length-at-age and length-to-weight parameters
from North Carolina and one using parameters from Little Cayman. Their
results show that using different parameters caused up to a four-year
difference in the time required for the simulated lionfish population to
recover to 90\% of its initial biomass after removals ceased. Here, we
show that using one set of length-weight parameters versus another for a
given length can result in more than a threefold under- or
overestimation of total weight. These differences become especially
important when allocating resources for lionfish removal programs,
incentivizing lionfish fisheries as a source of alternative livelihoods,
or estimating ecosystem impacts. Research efforts focused on invasive
lionfish populations need to use parameters calculated for their region
to the extent possible, or use different sets of parameters that provide
appropriate upper and lower bounds in their results.

>>>>

\usepackage{float}
\floatplacement{figure}{H}
\title{Spatial variation in allometric growth of invasive lionfish has
management implications}

@@

\begin{abstract}
Lionfish (\textit{Pterois volitans / miles}) are an invasive species in
the Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate total biomass estimates, which
depend on accurate estimates of allometric growth, but sedentary species
like lionfish often exhibit high levels of spatial variation in life
history characteristics. We reviewed 17 published length-weight
relationships for lionfish taken throughout their invasive range and
found regional differences that led to significant misestimates when
calculating weight from length observations. The spatial pattern we
observed is consistent with findings from other studies focused on
genetics or length-at-age. We show that the use of \textit{ex situ}
parameters can result in up to a threefold under- or overestimation of
total weight for an individual organism. When estimating total biomass,
the use of other parameters may produce estimates between 76.2\% and
140\% of true observed biomass. These findings can have implications for
management in terms of predicting effects on local ecosystems,
evaluating the effectiveness of removal programs, or estimating biomass
available for harvest.
\end{abstract}

@@

Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
in the Western Atlantic Ocean and Caribbean Sea, likely introduced
through release of aquarium-kept organisms \citep{betancurr_2011}.
Lionfish are the first invasive marine vertebrates established along
these coasts \citep{schofield_2009,schofield_2010,sabidoitza_2016}, and
they have established invasive populations in coral reefs, estuaries,
mangroves, hard-bottomed areas, and mesophotic reefs
\citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.
Their presence has been labeled as a ``major marine invasion'' because
they threaten local biodiversity, spread rapidly, and are difficult to
manage \citep{hixon_2016}.

@@

We reviewed 12 published studies and obtained 17 length-weight
relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}).
Study sites included North Carolina, the Northern and Southern Gulf of
Mexico, the Southern Mexican Caribbean, the Bahamas, Little Cayman,
Jamaica, Bonaire, Puerto Rico, and Costa Rica
\citep{barbour_2011,darling_2011,deleon_2013,fogg_2013,dahl_2014,edwards_2014,toledohernndez_2014,sandel_2015,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,chin_2016}.
We have access only to the summarized information published in these
studies - not the raw data authors used to make length-weight
calculations. We collected information on sex differentiation, location,
length and depth ranges, and sampling methods from each study when
available. Only two studies reported sex-specific length-weight
parameters \citep{aguilarperera_2016,fogg_2013}, so we assumed data were
reported for both sexes combined in all other studies. Reviewed studies
presented information for organisms ranging from 25-475 mm in Total
Length (\(TL\)) and were obtained at depths between 0.5 m and 57 m. Four
studies explicitly stated that their organisms were sampled with pole
spears \citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016},
and six studies mentioned that some of their organisms were obtained
with pole spears (or other type of harpoon) but also hand-held nets or
fish traps
\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016}.
Two studies did not specify how organisms were sampled
\citep{darling_2011,deleon_2013}.

@@

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here (Fig \ref{fig:all_allo}). Recall that the objective of
this study is not to describe variations between populations (which
would require access to raw data), but rather to assess how \emph{ex
situ} parameter values influence the accuracy of weight estimates for
lionfish, using the central Mexican Caribbean as a case study. Using
each of the 18 parameter pairs, we estimated \(TW\) from the \(TL\)
observations collected in the central Mexican Caribbean (n = 109, with
\(TL\) ranging from 34 mm to 310 mm) and divided predicted weights by
known observed weights to obtain a simple measure of over- or
underestimation. Difference in mean weight ratios were tested with an
analysis of covariance (ANCOVA):

\begin{equation}
R_{i,j} = \tilde{\mu} + \alpha_j + \beta TL_{ij} + e_{ij}
\end{equation}

Where \(R_{ij}\) is the weight ratio for the \(i\)-th organism obtained
with parameters from the \(j\)-th study, \(\tilde{\mu}\) is a constant
for all individuals, \(a_j\) is the treatment effect (\emph{i.e.} the
difference induced by each study), \(TL_{ij}\) is the covariate
(\emph{i.e.} Total Length) for the \(i\)-th subject in the \(j\)-th
group with slope \(\beta\), and \(e_{ij}\) is the error term of the
regression. Ratios were logit-transformed prior to analysis, and a
\emph{post-hoc} Tukey's test was used to identify groups where mean
ratios did not differ. All analyses were performed in R version 3.5.2
\citep{rcore_2018}. Raw data and code used in this work are available on
github at github.com/jcvdav/lionfish\_biometry.

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-2}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both sexes combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
\centering
\begin{tabular}{llllrll}
\toprule
Region & Sex & n & a & b & $R^2$ & Reference\\
\midrule
Western Atlantic & B & 774 & 2.90 & 2.89 & - & Barbour et al., 2011\\
Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
Caribbean & B & 458 & 3.60 & 2.81 & - & Sandel et al., 2015\\
Caribbean & B & 419 & 2.80 & 2.85 & 0.87 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.30 & 2.89 & 0.92 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.30 & 3.24 & 0.97 & Edwards et al., 2014\\
Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.80 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
\bottomrule
\end{tabular}
\end{table}

@@

The length-weight relationship for organisms from the central Mexican
Caribbean (\ref{fig:l-w-carib}) resulted in coefficient values of
\(a = 3.205 \times 10^{-6}\) and \(b = 3.235\) (\(R^2 = 0.977\),
\(F_{1, 107} = 6928.67; p < 0.001\)). The allometric factor (\(b\)) was
significantly different from \(b = 3\) (\(t_{107} = 6.04; p<0.001\)),
corroborating that lionfish present allometric growth. The length-weight
coefficients estimated here were within the range identified by studies
from other regions (Table \ref{tab:all_params}).

@@

ANCOVA results show that there were significant differences in our
predicted weight ratios for the central Mexican Caribbean when using
each of the different pairs of parameters
(\(F_{17, 1943} = 24.96; p < 0.001\); Fig \ref{fig:bio_ratio}). For
example, the actual observed weights of the 109 lionfish from the
Central Mexican Caribbean had a mean \(\pm\) SD of 52.56 \(\pm\) 76.58
g. However, if we used allometric parameter values from Banco Chinchorro
in the Caribbean to predict weights from our observed length
observations, we estimated a mean \(\pm\) SD of 40.37 \(\pm\) 58.74 g
\citep{sabidoitz_2016}. If we similarly used parameter values from North
Carolina in the Western Atlantic to estimate lionfish weights in the
Central Mexican Caribbean, we found a mean \(\pm\) SD 73.76 \(\pm\)
96.11 g \citep{barbour_2011}. Weights predicted from these extreme
parameters correspond to mean predicted-to-observed weight ratios of
0.80 \(\pm\) 0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.
Furthermore, for individual organisms, the largest differences between
predicted and observed values resulted in ratios of 0.36 and 3.51
(\emph{i.e.} the tails of each violin in Fig \ref{fig:bio_ratio}). If
instead of looking at the mean ratios we looked at the total biomass
(\emph{i.e.} summing across organisms), these cases would lead to
estimated total biomasses of 76.2\% (4,363.53 g) and 140\% (8,039.96 g)
of true observed biomass (5,729.34 g). These were the two most extreme
sets of parameters, but results consistently varie Use of \emph{ex situ}
parameters can result in erroneous weight and total biomass estimates
for lionfish.

Tukey's \emph{post-hoc} test suggested that weight ratios for the
central Mexican Caribbean were not different from those obtained with
parameters from Little Cayman, the Bahamas, and some sites in the Gulf
of Mexico (Tukey's HSD \(p > 0.05\)). All weight estimates using
parameters from the Gulf of Mexico and Western Atlantic were higher than
observed values, and only parameters from the Caribbean produced weights
smaller than observed (Fig \ref{fig:bio_ratio}). The regional average
(\(\pm\) SD) of predicted-to-observed weight ratios from these three
regions were 1.24 \(\pm\) 0.309, 1.41 \(\pm\) 0.523, and 1.20 \(\pm\)
0.423 for the Gulf of Mexico, Western Atlantic, and Caribbean,
respectively. This suggests that the smallest errors are observed when
using parameters from other locations in the Caribbean.

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/pred_obs-1.pdf}
\caption{\label{fig:bio_ratio}Violin plot of predicted-to-observed
weight ratios for 18 pairs of allometric parameters. Sex is indicated in
parentheses. Blue circles indicate median values and like letters
indicate values that do not differ significantly. For Sabido-Itza et al,
2016b, BC and PNAX make reference to Banco Chinchorro and Parque
Nacional Arrecifes de Xcalak, two sites for which they report
parameters.}
\end{figure}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:errors}Estimated total biomas relative to observed
biomass (5,729.34 g) for 18 pairs of allometric parameters. Sex is
indicated in parentheses. For Sabido-Itza et al, 2016b, BC and PNAX make
reference to Banco Chinchorro and Parque Nacional Arrecifes de Xcalak,
two sites for which they report parameters.}
\end{figure}

@@

Applying parameter estimates to lengths outside the range of lengths
originally used to estimate the parameters may also induce error. Our
smallest observed organism was 34 mm in \(TL\), and only two studies
estimated parametrs with smaller organisms
\citep{edwards_2014,sabidoitza_2016}. By contrast, our largest organism
had a \(TL\) of 310 mm, which is well within the range of all other
studies (the next smallest maximum length was 325 mm; See Supplementary
Table 2). Due to the power function describing the allometric
relationship (\emph{i.e.} Eq. 1), the error in weight estimates is
larger when extrapolation is done for lengths that are larger than the
maximum length used to estimate the parameters. Our estimates are
therefore conservative because we only used parameter pairs from other
studies to estimate weights for lionfish up to 310 mm in the Central
Mexican Caribbean, well within the range of lengths for which other
parameters were estimated.

The results presented here have key implications for management. For
example, \citet{edwards_2014} simulated a lionfish culling program under
two scenarios, one using length-at-age and length-to-weight parameters
from North Carolina and one using parameters from Little Cayman. Their
results show that using different parameters caused up to a four-year
difference in the time required for the simulated lionfish population to
recover to 90\% of its initial biomass after removals ceased. Here, we
show that using one set of length-weight parameters versus another for a
given length can result in more than a threefold under- or
overestimation of total weight for individual fish, and that total
biomass estimates may range between 76\% and 140\% of true observed
biomass. These differences become especially important when allocating
resources for lionfish removal programs, incentivizing lionfish
fisheries as a source of alternative livelihoods, or estimating
ecosystem impacts. Research efforts focused on invasive lionfish
populations need to use parameters calculated for their region to the
extent possible, or use different sets of parameters that provide
appropriate upper and lower bounds in their results.

### 2019-02-09 docs/reviews.Rmd
Added comments by Sean, and new figure

---
title: "Revision of MS #2018:11:32569:0:0:REVIEW"
output: pdf_document
---
<!-- BE REALLY CAREFUL to go through this and make sure the lines actually match up with the lines in the new manuscript - double check every one --> 
Dear Dr. Pawlik

@@

*As suggested by Rev2, we have logit-transformed our ratios and now evaluate them using an ANCOVA with study and total length as sources of variation.*

@@

*We have changed the word from "major" to "substantial" in L19 and L142 (now L139) and "key" in L175 (now L193). We chose to keep the word "major" in L26 to maintain consistency with the authors' original wording.*

@@

*The text now correctly states the research was performed in the Bahamas.*

@@

*We have improved the wording in the original sentence and no longer use the word "know"/"known".*

@@

*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L78-79) and Table 2 (now Table 1) reflect these changes.*

@@

*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L120.*

@@

*We have included the URL in the main text, but the decision to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*

>>>>

---
title: "Revision of MS #2018:11:32569:0:0:REVIEW"
output: pdf_document
---
Dear Dr. Pawlik

@@

*As suggested by Rev2, we have logit-transformed our ratios and now evaluate them using an ANCOVA, with study and total length as sources of variation.*

@@

- *We have removed the word from "major" from L19 (now L20).*

- *We chose to keep the word "major" in L26 to maintain consistency with the authors' original wording, but we have included quotations to denote this.*

- *In L142 (Now L145) We now say that "ex situ parameters can result in erroneous weight estimates"*

- *Ass suggested, we have changed "major" from L175 to "key" (now L201).*

@@

*The text now correctly states the research was performed in the Bahamas (L38).*

@@

*We have improved the wording in the original sentence and no longer use the word "know"/"known" (L59).*

@@

*The Bahamas are now reported as part of the Western Atlantic Ocean. Text in L82 (now L80-81) and Table 2 (now Table 1) reflect these changes.*

@@

*We have modified this so it reads "with TL ranging from 34 mm to 310 mm" in what is now L119.*

@@

*We have included the URL in the main text (L128), but the decision to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*
